Appendix 6: sdmTMB model validation and speed-testing methods

### 2021-12-22 doc/appendix-validation.Rmd
Edit appendix

---
title: "Appendix X: sdmTMB validation"
output:
  bookdown::pdf_document2:
    toc: false
number_sections: false
fig_caption: true
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

@@

```{r}
library(sdmTMB)
```

@@

# Penalized smoothers

@@

## `s(x)`

@@

@@

## `s(x1, by = x2)`

@@

## `s(x, y)`

@@

# IID random intercepts

@@

# Simulation-testing with various observation families

@@

>>>>

---
title: "Appendix 6: sdmTMB model validation and speed-testing methods"
output:
  bookdown::pdf_document2:
    toc: true
number_sections: false
fig_caption: true
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

@@

# Overall description of sdmTMB validation

@@

## Penalized smoothers

@@

### `s(x)`

@@

```{r, echo=TRUE}
library(sdmTMB)
```

@@

### `s(x1, by = x2)`

@@

### `s(x, y)`

@@

## IID random intercepts

@@

## Simulation-testing with various observation families

@@

# Supplemental methods for speed-testing related packages

TODO: Fig. 2 methods description
